Efficient Coalition Formation \\ for Web Services

### 2013-12-02 papers/coalition-journal-extension/coalition_journal.tex
fixes

\subsection{Cooperative Game Concepts}
Cooperative game is a branch of game theory that studies
strategies of self-interested entities or agents in a setting
where those agents can increase their payoff by binding agreements
and cooperating in groups. We let $N$ be a set of players. Any
subset $S$ of $N$ can form a group called $coalition$. A
\emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
coalition to a real number $v(S)$, the worth of $S$. This number
usually represents the output or payoff or again the performance
of these players working together as coalition.  If a coalition
$S$ is formed, then it can divide its worth, $v(S)$ in any
possible way among its members. The payoff vector $x \in
\mathbb{R}^S$ is the amount of payoff being distributed among the
members of the coalition $S$. The payoff vector satisfies two
conditions:

\begin{itemize}
    \item $x_i \geq 0$ for all $i \in N$, and
    \item $\sum_{i \in S} x_i \leq v(S)$
\end{itemize}

The second criteria is called the \emph{feasibility} condition,
according to which, the payoff for each agent cannot be more than
the coalition total gain. A payoff vector is also \emph{efficient}
if the payoff obtained by a coalition is distributed amongst the
coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
the characteristic function works in \emph{transferable utility}
(TU) settings, where utility (i.e., payoff) is transferable from
one player to another, or in other words, players have common
currency and a unit of income that is worth the same for all players
\cite{myerson1991game}.

@@

\emph{Shapley value} is a unique and fair solution concept for
payoff distribution among the members of the coalition. It
basically rewards members with the amount of marginal contribution
they have to the coalition.

@@

In this section, we present the web service and community coordinator's intractions, the task distribution process and revenue models in web service communities.

\subsection{Task destribution}

As mentioned in section \ref{webservice-communities}, communities are robust service providers with well stablished market share and reputation. By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks. The community master is characterizd by a request rate $(R_C)$ from users. Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $Tr_{ws}$ is excluded. This exclusion allows us to build our analysis on the particular value of $Tr_{ws}$. Throughput is the average rate of tasks a web service can perform per time unit. Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $Tr_{ws}$.

The community master uses a slightly modified \emph{weighted fair queuing} method to distribute task among its members. The goal is to allocate incoming tasks to web services with a rate matching throughput value of $Tr_{ws}$. In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than summation of throughput values of web services, some of the input tasks will be queued and served with delay. Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Tr_{ws})}$ when $\sum_{ws}{Tr_{ws}} \leq R_{C}$. However, when the community has more web services having more total throughput value than community's request rate $(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Tr_{ws}}{\sum_{ws}{Tr_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate.

While distributing tasks, the community master can verify the performance, throughput and quality of tasks being performed by web services. It can recognize if web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in quality metrics or throughput, the master community will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations and also penalize them. Therefor its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it's important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

The communities and web services earn revenue by performing tasks. The total gain is function of quality ($QoS_{ws}$) and quantity ($Tr_{ws}$) of tasks being performed. As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}. We have adopted a linear equal weigth average over all QoS parameteres listed in table \ref{qosws} excluding the $Throuput$ and $Cost$ parameters. A community has the option to weight specific QoS patameters more or less depending on the expectations of their clients.

The maximum potential output $(PO(C))$ of a community is aggregation of number of tasks, times their quality, for each web service participating as a member of the community:

@@

If the summation of throughput ($Tr_{ws}$) values of community members exceeds the input task rate of the community ($R_C$) the community cannot perform at its maximum potential. It means community has more web services than it needs for performing input task load. Therefore, in these cases, the actual output has to be normalized to the ammount of tasks being performed.

@@

The revenue function of the web service community, is a linear function of $Out(C)$ with a positive constant multiplier.

@@

In this section, we analyse a few numerical examples and discuss the motivation of web services and community intractions and the strategies they can adopt and the revenue they can earn adopting different strategies.

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Three web services of example 1}
\label{example_1}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 4 & 3.2\\
2 & 0.8 & 5 & 4.0\\
3 & 0.8 & 3 & 2.4\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_1_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
$\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 6.8\\
$\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
$\left\{1,2,3\right\}$ & 8.0\\
\hline
Community $R_C$: 12\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Three web services of example 2}
\label{example_2}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 5 & 4.0\\
2 & 0.7 & 6 & 4.2\\
3 & 0.7 & 4 & 2.8\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_2_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
$\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
$\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
$\left\{1,2,3\right\}$ & 7.3\\
\hline
Community $R_C$: 10\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}. The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community. The first table in figure \ref{example_1} lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their $Th_{ws}$ throughput value. The second table shows all the possible communities and their worth. The values suggest, communities having more web services have better gain and output. However community tries to distribute the gain between web services. Sometimes it is impossible to share the gain between all web services in a way no subset of them would individually gain more if they had their own group. In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, with ${ws_3}$ joining the community the value of community increases to 8.0. However there is no way to distribute the value among web services, where ${ws_1}$ and ${ws_2}$ can earn 7.2, and ${ws_3}$ earn at least 2.4, which they could earn before joining the community. This makes the group unstable. In the example of table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the value of community. The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community. In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Three web services of example 3}
\label{example_3}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
\hline
1 & 0.8 & 10 & 5\\
2 & 0.8 & 20 & 5\\
3 & 0.8 & 30 & 5\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_3_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{C_1\right\}$ & 0 & $\left\{C_2\right\}$ & 0\\
$\left\{C_1, ws_1\right\}$ & 8 & $\left\{C_2, ws_1\right\}$ & 8\\
$\left\{C_1, ws_2\right\}$ & 16 & $\left\{C_2, ws_2\right\}$ & 16\\
$\left\{C_1, ws_3\right\}$ & 16 & $\left\{C_2, ws_3\right\}$ & 24\\
$\left\{C_1, ws_1, ws_2\right\}$ & 16 & $\left\{C_2, ws_1, ws_2\right\}$ & 24\\
$\left\{C_1, ws_1, ws_3\right\}$ & 16 & $\left\{C_2, ws_1, ws_3\right\}$ & 32\\
$\left\{C_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_2, ws_2, ws_3\right\}$ & 32\\
$\left\{C_1, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_2, ws_1, ws_2, ws_3\right\}$ & 32\\
$\left\{C_1, C_2, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
\hline
Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Now we consider another example, in which we have different communities with different market share, ${R_C}$ values. Web services also have a small share of market independently, providing them with a small task pull. In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the \emph{social welfare}. In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$. In these types of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition. The communities usually start the game having some established members, encountering new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant. In this example if we initially having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_1}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_2}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.

@@

As mentioned in previous section, the worth and output of a
community of web services is a function of the
throughput and provided QoS. If the throughput rate is more than
the master's input request rate, it means the web services inside
the community are capable of serving more requests than the
demand. Considering this factor, the valuation function is
designed to balance the output performance so that it matches the
exact throughput rate and QoS the web service can provide within
the particular community.
%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests. **

@@

Considering $S \subseteq T$:
\setlength{\abovedisplayshortskip}{2pt}
\begin{gather*}
S \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
\\
T = (S \cup \left\{i\right\}) \cap T
\end{gather*}

@@

Our algorithm works as follows. We have an established community
with a master and some member web services already residing in the
community. A web service would send a join request to the
community. The ideal solution would be analyzing the \emph{core}
or \emph{$\epsilon$-core} stability of the group having this new
member. As the normal core membership algorithm is computationally
intractable, we exploit Proposition \ref{proposition1} and Equation
\ref{eq:convex_snow} to check the convexity of our game having
characteristic function where the new member is added. In the
equation, we set $C$ to be our community members $(C)$ before
having the new web service. We assign ${i}$ to the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service join our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

@@

It is possible to develop an anytime algorithm by continuing the
verification of this condition against all subsets of size $3$,
$4$, etc. until the algorithm gets interrupted.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools (see Figure \ref{fig_sim2}). Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the used
algorithms \cite{Sandholm1999209,
DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

@@

In this scenario, as new web services are discovered and get ready
to join communities, our algorithm keeps merging and splitting
partitions based on the preference function. The decision to merge
or split is based on the fact that all players must benefit. The
new web services will merge with communities if $all$ the players
are able to improve their individual payoff, and some web services
may split from old communities, if splitting does not decrease the
payoff of any web service of the community. According to
\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
and splitting will converge to a final partition, where web
services cannot improve their payoff. More details of this
algorithm and analysis of generic solutions on coalition formation
games are described in \cite{DBLP:journals/igtr/AptW09}.

\subsection{Taxtation, Subsiding and Community Stability}\label{s:tax}

We discuessed $core$ as one of the preminent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating. Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap. One reason is that there is always the possibility that the agents may leave the community or they may under perform from the quality values they were initially performing with.

>>>>

\subsection{Cooperative Game Concepts}
Cooperative game is a branch of game theory that studies
strategies of self-interested entities or agents in a setting
where those agents can increase their payoff by binding agreements
and cooperating in groups. We let $N$ be a set of players which can form a group called a $coalition$. A
\emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
coalition to a real number $v(N)$, the worth of $N$. This number
usually represents the output or payoff or again the performance
of these players working together as coalition.  If a coalition
$S$ is formed, then it can divide its worth, $v(N)$ in any
possible way among its members. The payoff vector $x \in
\mathbb{R}^N$ is the amount of payoff being distributed among the
members of the coalition $N$. The payoff vector satisfies two
conditions:

\begin{itemize}
    \item $x_i \geq 0$ for all $i \in N$, and
    \item $\sum_{i \in N} x_i \leq v(N)$
\end{itemize}

The second criteria is called the \emph{feasibility} condition,
according to which, the payoff for each agent cannot be more than
the coalition total gain. A payoff vector is also \emph{efficient}
if the payoff obtained by a coalition is distributed amongst the
coalition members: $\sum_{i \in N} x_i = v(N)$. This definition of
the characteristic function works in \emph{transferable utility}
(TU) settings, where utility (i.e., payoff) is transferable from
one player to another, or in other words, players have common
currency and a unit of income that is worth the same for all players
\cite{myerson1991game}.

@@

\emph{Shapley value} is a unique and fair solution concept for
payoff distribution among the members of the coalition. It
basically rewards members with the amount of average marginal contribution
they add to the coalition. It checks the contribution of member $i$ by adding the agent, to all possible subsets 
of coalitions $S$, where ${S \subseteq N\left\backslash\left\{i\right\}$. If he is added to the set $S$, his 
contribution to the coalition is $v(S \cup \left\{i\right\}) - v(S)$. Average marginal contribution of agent $i$'s 
is calculated by averaging this value over all possible subsets of $N$, in $Shapley value$ equation (\ref{eq:shapley}).

@@

In this section, we present  web services and community coordinator's interactions, the task distribution process and revenue models in web service communities.

\subsection{Task distribution}

As mentioned in section \ref{webservice-communities}, communities are robust service providers with well established market share and reputation. By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks. The community master is characterized by a request rate $(R_C)$ from users. Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is excluded. Throughput is the average rate of tasks a web service can perform per time unit. Its exclusion from $QoS_{ws}$ allows us to build our analysis on the particular value of $Th_{ws}$. Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $Th_{ws}$.

The community master uses a slightly modified \emph{weighted fair queuing} method to distribute tasks among its members. The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$. In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with delay. Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Th_{ws})}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. However, when the input rate $(R_C)$ of the community is less than the summation of throughput values of the web services in the community,
%the community has more web services having more total throughput value than community's request rate 
$(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate.

While distributing tasks, the community master can verify the performance, throughput and quality of service of   tasks being performed by web services. It can recognize if web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in quality metrics or throughput, the  community master will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations but also to penalize them.
In this way, players have incentive to reveal their real capabilities to profit best from the community and to avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may  degrade or improve, a change that the community should adjust to. 
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

The communities and web services earn revenue by performing tasks. The total gain is function of quality ($QoS_{ws}$) and throughput ($Th_{ws}$) of tasks being performed. As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}. We have adopted a linear equal weight average over all QoS parameters listed in table \ref{qosws} excluding the $Throughput$ and $Cost$ parameters. A community has the option to weigh specific QoS parameters depending on the expectations of their clients.

The maximum potential output of a community $(PO(C))$  is an aggregation of number of tasks, times their quality, for each web service member of the community:

@@

If the summation of throughput values ($Th_{ws}$) of community members exceeds the input task rate of the community ($R_C$) the community cannot perform at its maximum potential. It denotes the case when the community has more web services than it needs to perform the input task load. The actual output has to be normalized to the amount of tasks being performed.

@@

The revenue function of the web service community is a linear function of $Out(C)$ with a positive constant multiplier.

@@

In this section, we analyze three numerical examples and discuss the motivation of web services and community interactions and the strategies they can adopt and the revenue they can earn adopting these different strategies.

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 1}
\label{example_1}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 4 & 3.2\\
2 & 0.8 & 5 & 4.0\\
3 & 0.8 & 3 & 2.4\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_1_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
$\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
$\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
$\left\{1,2,3\right\}$ & 8.0\\
\hline
Community $R_C$: 10\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 2}
\label{example_2}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 5 & 4.0\\
2 & 0.7 & 6 & 4.2\\
3 & 0.7 & 4 & 2.8\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_2_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
$\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
$\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
$\left\{1,2,3\right\}$ & 7.3\\
\hline
Community $R_C$: 10\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%, %%%%%%%%%%%%%%%%%%%%%%

In the first example,  we present the case of a community with $R_C =10 $, and three web services, each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}. The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community. The first table  lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their  throughput value $Th_{ws}$. The second table shows all the possible communities and their respective worth. The obtained values suggest that  communities having more web services have better gain and output. However each community needs to  distribute the gain between web services. Sometimes it is impossible to share the gain between all web services in a way that no subset of them would individually gain more if they form their own group. In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, With ${ws_3}$ joining the community the worth increases to 8.0. However there is no way to distribute the value among web services to have  ${ws_1}$ and ${ws_2}$  earning 7.2, and ${ws_3}$ earning at least 2.4, the gain they could earn before joining the community. This fact makes the group unstable. In the second  example, shown in table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the value of community. The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community. In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Example 3}
\label{example_3}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
\hline
1 & 0.8 & 10 & 5\\
2 & 0.8 & 20 & 5\\
3 & 0.8 & 30 & 5\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_3_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Worth & Community & Worth\\
\hline
$\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
$\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
$\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
$\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
$\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
$\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
$\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
$\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
$\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
\hline
Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Example 3, we consider the case of having different communities with different market share, ${R_C}$ values. Web services also have a small share of market independently, providing them with a small task pull. In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the \emph{social welfare}. In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$. In these types of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition. The communities usually start the game having some established members, encountering new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant. In this example if we initially having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_{master_1}}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_{master_2}}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.

@@

As mentioned in previous section, the worth and output of a
community  is a function of the
throughput and provided QoS of its web service members. If the throughput rate is more than
the master's input request rate, it means the web services inside
the community are capable of serving more requests than the
demand. Considering this factor, the valuation function is
designed to balance the output performance so that it matches the
exact throughput rate and QoS the web service can provide within
the particular community.
%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests. **

@@

Considering $S \subseteq T$:
\setlength{\abovedisplayshortskip}{2pt}
\begin{gather*}
T \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
\\
S = (S \cup \left\{i\right\}) \cap T
\end{gather*}

@@

Our algorithm works as follows. Given an  established community
with a master and some member web services, a web service would send a \emph{join request} to join  the
community. Ideally, the \emph{core}
or \emph{$\epsilon$-core} stability of the group having this new
member should be analyzed. As the normal core membership algorithm is computationally
intractable, we exploit Proposition \ref{proposition1} and Equation
\ref{eq:convex_snow} to check the convexity of our game having
characteristic function where the new member is added. In the
equation, let $C$  be our community members before
having the new web service join the community. Let  ${i}$ be the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service join our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

@@

It is possible to develop  algorithm that continues the
verification of this condition against subsets of size $3$,
$4$, etc. until the algorithm gets interrupted.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools (see Figure \ref{fig_sim2}). Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the used
algorithms in \cite{Sandholm1999209,
DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

@@

In this scenario, as new web services are discovered and get ready
to join communities, our algorithm keeps merging and splitting
partitions based on the preference function. The decision to merge
or split is based on the fact that all players must benefit. The
new web services will merge with communities if $all$ the players
are able to improve their individual payoff, and some web services
may split from old communities, if splitting does not decrease the
payoff of \emph{any} web service of the community. According to
\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
and splitting will converge to a final partition, where web
services cannot improve their payoff. More details of this
algorithm and analysis of generic solutions on coalition formation
games are described in \cite{DBLP:journals/igtr/AptW09}.

\subsection{Taxation, Subsiding and Community Stability}\label{s:tax}

We discussed $core$ as one of the prominent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal amount of $\epsilon$ by deviating. Stability is an attractive property for communities. In addition, communities would benefit by having slightly more web services then the exact number of web services satisfying task rate cap. This is because  there is always a possibility that the agents may leave the community or they may under perform and degrade the quality values they were initially performing with.

One way for communities to ensure  stability could be  by applying a tax, $\epsilon$ amount of cost for web services changing communities which would make deviation a costly act. However this would require all community coordinators to agree on a same amount of taxation, being governed by some external entities or web services would join communities with lesser amount of tax. Another viable solution to our scenario is to stabilize the game using external subsidies. The reason a game is not stable is that the community is not making enough revenue to allocate  enough gain to the players. A community master can subside its community with a constant coefficient value of $\lambda$.

Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.
